On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-07-19 Manuscript/manuscript.tex
added table comparing the 3 models and their probabilities for each dataset

@@

\section{Discussion}\label{sec:Discussion}
Since 1985 Seiko Holding Corporations has served every World Athletics 
Championships as the official timer \citep{wa2022seiko}.  Since 1985, the 
technology and the ability to accurately predict measurements: long jump 
distances, false starts, total time, reaction time, etc. have all dramatically 
improved.  Seiko did not start tracking reaction time as an official measurement
until 1999 in the men's 110 meter hurdles and women's 100 meter hurdles. 
Seiko regularly updates their equipment so that they provide cutting edge
technology to the World Track and Field Championships, the highest stakes in the 
world of running outside of the Olympics. Seiko's technology for detecting 
reaction times relies on the pressure that athletes exert on the plate when they 
push off.  Their systems measure the time differential between when the ``gun" 
goes off to start the race and when the pressure changes \citep{wa2022seiko}.  
If an athlete has a reaction time under 0.1 seconds, it is deemed a false start 
as it is considered that no athlete can react so quickly \citep{Seiko-Timing}.  
Thus, a reaction time of for example 0.05, suggests that the athlete predicted 
the gun and it was luck that caused their abnormally high time.  At the World 
Championships level, World Athletics and Seiko want to remove that element of 
luck and thus impose the 0.1 second barrier. In 2013, Seiko upgraded their 
timing equipment for sprinting events (110 meter hurdles falls under this 
category) \citep{wa2013backtage}. Since 1999, the slowest reaction times in the 
men's 110-meter hurdle were recorded in 2013.  That is not to say that the higher 
times were caused by Seiko's equipment, but the two may be related.  It is worth 
noting that prior to 2022, Seiko again upgraded its technology but for its jump 
management system. 
\eds{I would argue that this paragraph should go in the discussion as there are 
no results presented here}
\of{I agree so I moved it here. Not sure if it belongs at the top of the
discussion or elsewhere but here it is.}

>>>>

\jy{label the table and reference to it; clean it up}
\begin{table}
  \centering
  \caption{Compares the various effect models by dataset, all probabilities are
  for observing a reaction time less than 0.1 seconds. In general the model with
  the highest probability (least extreme reaction time) is the Year Effect model.}
  \begin{tabular}{c c c c} 
   \toprule
   Data Set & Year Effect & Batch Effect & Both Effects \\ 
   \midrule
   Old Finals & $4.39\cdot10^{-4}$ & $4.24\cdot10^{-4}$ & $4.36\cdot10^{-4}$ \\
   All Finals & $8.63\cdot10^{-4}$ & $8.65\cdot10^{-4}$ & $8.64\cdot10^{-4}$ \\
   Old Pooled & $5.73\cdot10^{-3}$ & $5.21\cdot10^{-3}$ & $4.15\cdot10^{-3}$ \\ 
   All Pooled & $6.84\cdot10^{-3}$ & $6.64\cdot10^{-3}$ & $5.15\cdot10^{-3}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:EffectComparison}
\end{table}

@@

\section{Discussion}\label{sec:Discussion}
Since 1985 Seiko Holding Corporations has served every World Athletics 
Championships as the official timer \citep{wa2022seiko}.  Since 1985, the 
technology and the ability to accurately predict measurements: long jump 
distances, false starts, total time, reaction time, etc. have all dramatically 
improved.  Seiko did not start tracking reaction time as an official measurement
until 1999 in the men's 110 meter hurdles and women's 100 meter hurdles. 
Seiko regularly updates their equipment so that they provide cutting edge
technology to the World Track and Field Championships, the highest stakes in the 
world of running outside of the Olympics. Seiko's technology for detecting 
reaction times relies on the pressure that athletes exert on the plate when they 
push off.  Their systems measure the time differential between when the ``gun" 
goes off to start the race and when the pressure changes \citep{wa2022seiko}.  
If an athlete has a reaction time under 0.1 seconds, it is deemed a false start 
as it is considered that no athlete can react so quickly \citep{Seiko-Timing}.  
Thus, a reaction time of for example 0.05, suggests that the athlete predicted 
the gun and it was luck that caused their abnormally high time.  At the World 
Championships level, World Athletics and Seiko want to remove that element of 
luck and thus impose the 0.1 second barrier. In 2013, Seiko upgraded their 
timing equipment for sprinting events (110 meter hurdles falls under this 
category) \citep{wa2013backtage}. Since 1999, the slowest reaction times in the 
men's 110-meter hurdle were recorded in 2013.  That is not to say that the higher 
times were caused by Seiko's equipment, but the two may be related.  It is worth 
noting that prior to 2022, Seiko again upgraded its technology but for its jump 
management system. 
\eds{I would argue that this paragraph should go in the discussion as there are 
no results presented here}
\of{I agree so I moved it here. I think it also could fit into the top of the
data section as in section~\ref{sec:Data}. Thoughts?}
